---
title: "Analyses_Hypothesis"
author: "Christoph Völtzke"
date: "2023-01-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(readr)
library(DescTools)
library(lavaan)
library(tidyverse)
```


```{r}
data <- read_csv("Data/data.csv")
data <- data %>%
  rename(ID = "...1") %>%
  mutate(ID = as.character(ID),
         Condition = as.factor(Condition),
         Message_Int = as.factor(Message_Int),
         Task_Type = as.factor(Task_Type),
         NFHI_dicho = case_when(
           NFHI < mean(NFHI) ~ 0,
           NFHI >= mean(NFHI) ~ 1)
         )
```

```{r}
summary(data)
```

# Testing Main effects for Customer Satisfaction, Social Presence and Perceived Contingency
```{r}
# Running the ANOVA related to the plot and the research question. The ANOVA results should be used in additon to the plot in order to investigate the research question.
model1 <- aov(Customer_sat ~ Message_Int + Task_Type + Message_Int*Task_Type + Product_inv + Chat_use + NFHI, data = data)
summary(model1)
EtaSq(model1, type=2)
model2 <- aov(Perc_cont ~ Message_Int + Task_Type + Message_Int*Task_Type  + Product_inv + Chat_use+ NFHI, data = data)
summary(model2)
EtaSq(model2, type=2)
model3 <- aov(Social_pres ~ Message_Int + Task_Type + Message_Int*Task_Type  + Product_inv + Chat_use + NFHI, data = data)
summary(model3)
EtaSq(model3, type=2)
model4 <- aov(Orga_perc ~ Message_Int + Task_Type + Message_Int*Task_Type + Product_inv + Chat_use + NFHI, data = data)
summary(model4)
EtaSq(model4, type=2)
```
1. hypothesis H1 is supported
2.  hypotheses H2a,b, and H4a,b are supported

## Mediation analyses

Mediation with Process function by Hayes
```{r}
source("process.R")
```
```{r}
# Process needs numerical predictors. Therefore, the IVs are in the df two times. One time as a factor and one time as numeric
process(data = data, y = "Customer_sat", x = "Message_Int_n", m = c("Perc_cont","Social_pres"), model = 4, effsize =1, total =1, stand =1, cov = c("Product_inv", "Chat_use","NFHI"), boot = 10000 , modelbt = 1, seed = 123)
```
A-path to Perceived Contingency: 

Message_Int_n    1.6497    0.1654    9.9713    0.0000    1.3239    1.9755

A-path to Social Presence:
Message_Int_n    1.4942    0.1641    9.1077    0.0000    1.1712    1.8173

B-path both mediators:
Perc_cont        0.5934    0.0510   11.6349    0.0000    0.4930    0.6938
Social_pres      0.1564    0.0514    3.0414    0.0026    0.0551    0.2577

Indirect effects: 

TOTAL          1.2127    0.1547    0.9164    1.5312 
Total indirect effect. Indirect effects mediated by mediator 1 or 2 taken together. Bootstrapped, here it is significant since the CI does not contain zero.

Perc_cont      0.9789    0.1460    0.6982    1.2781
Indirect effect mediated by mediator 1. Bootstrapped, here it is significant since the CI does not contain zero.

Social_pres    0.2337    0.0718    0.1032    0.3878
Indirect effect mediated by mediator 2. Bootstrapped, here it is significant since the CI does not contain zero.

## Moderation - Task Type

```{r}
process(data = data, y = "Customer_sat", x = "Message_Int_n", m = c("Perc_cont","Social_pres"), w = "Task_Type_n", model = 8, cov = c("Product_inv", "Chat_use","NFHI"), boot = 10000 , center = 2,
moments = 1, modelbt = 1, seed = 123)
```

As the  Index of moderated mediation
     (differences beween conditional indirect effects):
                Index    BootSE  BootLLCI  BootULCI
Task_Type_n   -0.2523    0.2044   -0.6472    0.1601

Includes 0 it is not a significant mediated moderation.


## Moderation - Task Type

```{r}
process(data = data, y = "Customer_sat", x = "Message_Int_n", m = c("Perc_cont","Social_pres"), w = "NFHI_dicho", model = 8, cov = c("Product_inv", "Chat_use"), boot = 10000 , center = 2,
moments = 1, modelbt = 1, seed = 123)
```

As the Index of moderated mediation
     (differences beween conditional indirect effects):
               Index    BootSE  BootLLCI  BootULCI
NFHI_dicho   -0.0298    0.0552   -0.1484    0.0746

Includes 0 it is not a significant mediated moderation.

## Extra simple Moderation NFHI
```{r}
model5 <- aov(Customer_sat ~ Message_Int + Task_Type + Message_Int*NFHI_dicho +  Task_Type*NFHI_dicho + Product_inv + Chat_use , data = data)
summary(model5)
```

It is not moderating the effect, however it still has an influence on the outcome variable.

